openarchaeoCollaboration

### 2021-02-27 analysis/paper.Rmd
Add plot of commits through time
And reknit paper.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r dependencies, include=FALSE}
library("tidyverse")
library("openarchaeoCollaboration")
```

@@

```{r data-oarch}
read_csv("https://raw.githubusercontent.com/zackbatist/open-archaeo/master/open-archaeo.csv") %>% 
  mutate(category = na_if(category, "?")) %>% 
  mutate(gh_repo = str_remove(github, "https://github.com/")) ->
  oarch
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      layout = "l-body-outset")
```

```{r dependencies, include=FALSE}
library("tidyverse")
library("lubridate")
library("openarchaeoCollaboration")
```

@@

```{r data-oarch}
read_csv("https://raw.githubusercontent.com/zackbatist/open-archaeo/master/open-archaeo.csv") %>% 
  mutate(category = na_if(category, "?")) %>% 
  mutate(gh_repo = str_remove(github, "https://github.com/")) ->
  oarch

oarch <- mutate(oarch, rough_category = recode(category,
                                 "R" = "Packages (R, Python, etc.)",
                                 "Web apps" = "Standalone apps",
                                 "Datasets" = "Analyses & datasets",
                                 "Tutorials" = "Lists & tutorials",
                                 "Python" = "Packages (R, Python, etc.)",
                                 "Desktop apps" = "Standalone apps",
                                 "QGIS" = "Plugins",
                                 "Lists" = "Lists & tutorials",
                                 "Mobile apps" = "Standalone apps",
                                 "Analyses" = "Analyses & datasets",
                                 "Spreadsheets" = "Forms & spreadsheets",
                                 "Command line tools" = "Standalone apps",
                                 "Plugins" = "Plugins",
                                 "ArcGis" = "Plugins",
                                 "Filemaker" = "Plugins",
                                 "ODK" = "Forms & spreadsheets",
                                 "Lisp" = "Packages (R, Python, etc.)",
                                 .default = "Other",
                                 .missing = "Other"
                                 ))
```

@@

```{r plot-gh_commits-cum}
oarch %>% 
  unnest(gh_commits) %>% 
  drop_na(sha) %>% 
  mutate(date = floor_date(datetime, "week")) %>% 
  mutate(rough_category = recode(
    rough_category,
    "Standalone apps" = "Standalone apps",
    "Packages (R, Python, etc.)" = "Packages (R, Python, etc.)",
    .default = "Other")) %>% 
  group_by(rough_category, date) %>% 
  summarise(n_commits = n(), .groups = "drop_last") %>% 
  mutate(cat_total = sum(n_commits)) %>% 
  mutate(cum_commits = cumsum(n_commits)) %>% 
  ggplot(aes(date, cum_commits, 
             fill = fct_reorder(rough_category, cat_total))) +
  geom_area() +
  scale_x_datetime(limits = c(ymd("2008-01-01", tz = "UTC"), NA),
                   date_breaks = "2 years",
                   date_labels = "%Y") +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "Open source archaeology",
    subtitle = "Cumulative commits in GitHub repositories",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = NULL, y = "Commits", fill = NULL
  ) +
  theme(legend.position = "bottom")
```
